Robust Decorrelation of Errors in Quantum Gates by Random Gate Synthesis

### 2018-11-26 decorrelation/decorrelation.tex
Added figure

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{vectorspace.pdf}
  \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error. These error Hamiltonians lie in a vector space. a) Four effective Hamiltonians. The origin is not contained in their convex hull, so there are no balanced control solutions. b) The origin is contained in the covex hull after adding an additional control solution. Because there are more than $n+1$ implementations, there exist an infinite number of balanced control solutions. c) The error Hamiltonians shown with their derivative with respect to a control parameter. As this parameter drifts, a $0^{\rm th}$-order balanced control solution may drift, leading to a first-order error. d) The derivatives also lie in a vector space. If the origin lies in their convex hull, then it may be possible to construct a $1^{\rm{st}}$-order robust balanced control solution.}
  \label{fig:vectorspace}
\end{figure}
